\documentclass{report}
\usepackage[utf8]{inputenc}

\title{RGB-2-Gray image converter: cpu and gpu comparison}
\author{LE Nhu Chu Hiep}
\date{\today}

\begin{document}

\maketitle

\section{Introduction}

This is part of advancedhpc2022 course. We try to implement algorithm to convert rgb image to gray-scale image. It is just simple algorithm. But we implement it in 2 methods: first to run on cpu and second to run on gpu. Then we try to measure and compare elapsed time between 2 methods.

\section{CPU Implementation}

Do it simple with a loop and recompute each pixel. Following
below instruction:

\begin{enumerate}
    \item Load image
    \item Flatten image
    \item Build thread function to compute average value for each pixel
    \item Loop and create thread to compute whole image
    \item Run and wait for all threads join
    \item Re-shape image to original shape
    \item Shape image to new file
\end{enumerate}

Evaluation:

\beign{verbatim}
CPU Running...
Elapsed time: 10287.384271621704 ms
[DEBUG] saved gray image path: result/eiffel_cpu_gray.jpg
\end{verbatim}

\section{GPU Implementation}

GPU has too much of cores than CPU, we desire to leverage them to
improve time performance of converter process. Because GPU is treated as SIMD
architecture, it allows to execute single function (kernel) for all core at same
time with slightly different of thread index. Hence, we need to design a good kernel
to reach out our target. Depend on GPU architecture, we need to build a specific
algorithm for doing that. On this labwork, we suppose to use most simplest one.
We map each thread index corresponding to one pixel. Then each thread try to
do same job as CPU process on its own pixel. Detail algorithm is described below:

\begin{enumerate}
    \item Load input image (Color image) and output array (Gray image)
    \item Get thread index
    \item Checking whether thread index is valid mapped to a pixel
    \item If thread does not valid, it is closed
    \item If thread mapped to pixel, it compute average value of pixel saved to output image
    \item When all the thread done, return back output image to CPU
\end{enumerate}

Evaluation

\begin{verbatim}
GPU Running...
Elapsed time: 68.34006309509277 ms
[DEBUG] saved gray image path: result/eiffel_gpu_gray.jpg
\end{verbatim}

\end{document}
